Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex
Nit
Another grant

\paragraph*{Applicability to Roessler \& DeHon~\cite{DBLP:conf/sp/RoesslerD18}:}

@@

This work was supported by the National Science Foundation under Grant No. 2048499, Specifying and Verifying Secure Compilation of C Code to Tagged Hardware;
by Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) as part of the Excellence Strategy of the German Federal and State Governments, EXC 2092 CASA -- 390781972;
by NSF award \#2145649, CAREER: Fuzzing Formal Specifications,
by
NSF award \#1955610, Bringing Python Up To Speed,
and by %
NSF award \#1521523, Expeditions in Computing: The Science of Deep
  Specification.

>>>>

\paragraph*{Applicability to Roessler \& DeHon~\cite{DBLP:conf/sp/RoesslerD18}}

@@

This work was supported by the National Science Foundation under Grant No. 2048499, Specifying and Verifying Secure Compilation of C Code to Tagged Hardware;
by ERC Starting Grant SECOMP (715753), Efficient Formally Secure Compilers to a Tagged Architecture;
by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) as part of the Excellence Strategy of the German Federal and State Governments, EXC 2092 CASA -- 390781972;
by NSF award \#2145649, CAREER: Fuzzing Formal Specifications,
by
NSF award \#1955610, Bringing Python Up To Speed,
and by %
NSF award \#1521523, Expeditions in Computing: The Science of Deep
  Specification.
